Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-10-03 eqm_profiles.tex
add defn of MPE and description of state variables

For Markov-perfect equilibrium, strategy profile must be dependent on state variable, $q_{s}$ only.

>>>>

\vskip.5in	
According to Mailath and Samuelson (2006) p. 177.
\begin{itemize}
	\item The strategy profile $\sigma$ is a stationary Markov strategy if for any two ex post histories $\tilde{h}^t$ and $\tilde{h}^\tau$ (of equal or different lengths) terminating in the same state, $\sigma\left(\tilde{h}^t\right) = \sigma\left(\tilde{h}^\tau\right)$.
	\item The strategy profile $\sigma$ is a stationary Markov equilibrium if $\sigma$ is a stationary Markov strategy profile and a subgame-perfect equilibrium.
\end{itemize}

\vskip.5in
We have six state variables, so $s = \left(q_s,q_g,l_s,l_g,w_s,w_g \right)$.
\begin{itemize}
	\item Strategies are a function of all six state variables
	\item Strategies for the patron and $c$ are also how much to invest in each of the six state variables. Some can be ruled out by preference assumptions:
		\begin{itemize}
			\item $c$ dislikes war, so will never invest in $w_s$ or $w_g$. It would also not want to make the government lose, so won't invest in $l_g$ either.
			\item Because the patron's preferences are aligned with the secessionists and against the government, it never invests in $w_g$ or $l_s$.
		\end{itemize}
\end{itemize}
